---
title: "Project 3"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(ggplot2)
library(AER)
library(nleqslv)
library(pastecs)
```

```{r}
data <- read_csv("OTC_Data.csv")
```

```{r}
nrow(distinct(data,store)) 
#73 distinct stores

nrow(distinct(data,week)) 
# 48 distinct weeks

nrow(distinct(data,brand_name))*nrow(distinct(data,size)) 
# 9 distinct products

nrow(distinct(data,brand_name)) 
# 3 distinct brands
```

calculate total sales and total expenditure of each store-week as well as market share and expenditure share (wi). Stone index and 18 variables for price and cost.

```{r}
data2 <- data
data2 = data2[FALSE,]
options(digits=3)
for (i in unique(data$week)){
  for (j in unique(data$store)){
    test <- filter(data, week == i, store == j)   
    test <- test %>% mutate(sales_total = sum(test$sales), mkt_share = (sales/sales_total)) 
    
    ty <- filter(test, brand_name == "Tylenol")
    ad <- filter(test, brand_name == "Advil")
    ba <- filter(test, brand_name == "Bayer")
    
    ty_total = sum(ty$sales*ty$price)
    ad_total = sum(ad$sales*ad$price)
    ba_total = sum(ba$sales*ba$price)
    
    test <- test %>% mutate(exp_total = ifelse(brand_name == "Tylenol", ty_total, ifelse(brand_name == "Advil", ad_total, ifelse(brand_name == "Bayer",ba_total, "NA")))) 
    
    test$exp_total = as.numeric(as.character(test$exp_total))
    
    test <- test %>% mutate(exp_share = (price*sales)/exp_total)
    
    ty <- filter(test, brand_name == "Tylenol")
    ad <- filter(test, brand_name == "Advil")
    ba <- filter(test, brand_name == "Bayer")
    
    ty <- ty %>% mutate(lprice = log(price))
    ad <- ad %>% mutate(lprice = log(price))
    ba <- ba %>% mutate(lprice = log(price))
    
    ty_stone = sum(ty$exp_share*ty$lprice)
    ad_stone = sum(ad$exp_share*ad$lprice)
    ba_stone = sum(ba$exp_share*ba$lprice)
    
    test <- test %>% mutate(stone = ifelse(brand_name == "Tylenol", ty_stone, ifelse(brand_name == "Advil", ad_stone, ifelse(brand_name == "Bayer",ba_stone, "NA")))) 
    
    test$stone = as.numeric(as.character(test$stone))
    
    test <- test %>% mutate(ty25p = price[1],ty50p = price[2], ty100p = price[3], ad25p = price[4], ad50p = price[5], ad100p = price[6], ba25p = price[7], ba50p = price[8], ba100p = price[9])
    
    test <- test %>% mutate(ty25c = cost[1],ty50c = cost[2], ty100c = cost[3], ad25c = cost[4], ad50c = cost[5], ad100c = cost[6], ba25c = cost[7], ba50c = cost[8], ba100c = cost[9])
    
    data2 <- rbind(data2, test)
    }}
```

## summary statistics

```{r}
options(scipen=100)
options(digits=3)

## Tylenol
ty25 <- filter(data2, brand_name == "Tylenol", size == "25")
stat.desc(ty25, basic = F)
# price: mean 3.42, sd 0.271
# wholesale price: mean 2.182, sd 0.179
# market share: mean 0.178, sd 0.057

ty50 <- filter(data2, brand_name == "Tylenol", size == "50") 
stat.desc(ty50, basic = F)
# price: mean 4.942, sd 0.262
# wholesale price: mean 3.672, sd 0.182
# market share: mean 0.213, sd 0.0657

ty100 <- filter(data2, brand_name == "Tylenol", size == "100")
stat.desc(ty100, basic = F)
# price: mean 4.942, sd 0.262
# wholesale price: mean 3.672, sd 0.182
# market share: mean 0.140, sd 0.053

## Advil
ad25 <- filter(data2, brand_name == "Advil", size == "25")
stat.desc(ad25, basic = F)
# price: mean 2.964, sd 0.199
# wholesale price: mean 2.03, sd 0.071
# market share: mean 0.144, sd 0.052

ad50 <- filter(data2, brand_name == "Advil", size == "50")
stat.desc(ad50, basic = F)
# price: mean 5.145, sd 0.293
# wholesale price: mean 3.623, sd 0.142
# market share: mean 0.092, sd 0.055

ad100 <- filter(data2, brand_name == "Advil", size == "100")
stat.desc(ad100, basic = F)
# price: mean 8.160, sd 0.344
# wholesale price: mean 6.091, sd 0.226
# market share: mean 0.043, sd 0.030


## Bayer
ba25 <- filter(data2, brand_name == "Bayer", size == "25")
stat.desc(ba25, basic = F)
# price: mean 2.673, sd 0.322
# wholesale price: mean 1.847, sd 0.155
# market share: mean 0.051, sd 0.029

ba50 <- filter(data2, brand_name == "Bayer", size == "50")
stat.desc(ba50, basic = F)
# price: mean 3.607, sd 0.377
# wholesale price: mean 2.422, sd 0.349
# market share: mean 0.041, sd 0.027

ba100 <- filter(data2, brand_name == "Bayer", size == "100")
stat.desc(ba100, basic = F)
# price: mean 3.967, sd 0.185
# wholesale price: mean 3.712, sd 0.117
# market share: mean 0.097, sd 0.045
```


```{r}
options(scipen = 1)
fit1 <- lm(log(sales) ~ log(price), data2)
summary(fit1)
# price elasticity of demand is -0.1406
```

```{r}
# create 9 new dummy variables
data2 <- data2 %>% mutate(ty25 = ifelse(brand_name == "Tylenol" & size == 25,1,0 ), 
                          ty50 = ifelse(brand_name == "Tylenol" & size == 50,1,0 ), 
                          ty100 = ifelse(brand_name == "Tylenol" & size == 100,1,0), 
                          ad25 = ifelse(brand_name == "Advil" & size == 25,1,0),
                          ad50 = ifelse(brand_name == "Advil" & size == 50,1,0),
                          ad100 = ifelse(brand_name == "Advil" & size == 100,1,0), 
                          ba25 = ifelse(brand_name == "Bayer" & size == 25,1,0), 
                          ba50 = ifelse(brand_name == "Bayer" & size == 50,1,0), 
                          ba100 = ifelse(brand_name == "Bayer" & size == 100,1,0))
```

```{r}
# 27 interaction variables between log(price) and product dummies
n = 42
for (i in seq(33,35)){
  for (j in  seq(15,17)){
  data2[,n] = data2[,i]*log(data2[,j])
  n <- n + 1
  }
}

for (i in seq(36,38)){
  for (j in  seq(18,20)){
  data2[,n] = data2[,i]*log(data2[,j])
  n <- n + 1
  }
}

for (i in seq(39,41)){
  for (j in  seq(21,23)){
  data2[,n] = data2[,i]*log(data2[,j])
  n <- n + 1
  }
}

# 27 interaction variables between cost and product dummies for the IV model
for (i in seq(33,35)){
  for (j in  seq(24,26)){
  data2[,n] = data2[,i]*data2[,j]
  n <- n + 1
  }
}

for (i in seq(36,38)){
  for (j in  seq(27,29)){
  data2[,n] = data2[,i]*data2[,j]
  n <- n + 1
  }
}

for (i in seq(39,41)){
  for (j in  seq(30,32)){
  data2[,n] = data2[,i]*data2[,j]
  n <- n + 1
  }
}
```

## Lowest level stone price index

Estimate the lowest level of the model using the Stone price index and without assuming symmetry of the $\gamma$.

```{r}
data2 <- data2 %>% mutate(lxoverp = log(exp_total)-stone)

options(digits = 3)
n = 97
for (i in seq(33,41)){
  data2[,n] = data2[,i]*data2[,96]
  n = n + 1
}

# create a new data frame and keep only the columns in the regression.
data3 <- data2
data3[,c(1:12,14:32,69:96)]<- NULL

fit2 <- lm(exp_share ~ ., data3)
summary(fit2)
```

## Lowest level IV: wholesale price

Estimate the lowest level of the model using IV, with cost as the instrument
for price.

```{r}
data4 <- data2
data4[,c(1:12,14:32,96)]<- NULL
fit3 <- ivreg(exp_share ~ ty25 + ty50 + ty100 + ad25 + ad50 + ad100 + ba25 + ba50 + ba100 + ty25.1 + ty25.2 + ty25.3 + ty50.1 + ty50.2 + ty50.3 + ty100.1 + ty100.2 + ty100.3 + ad25.1 + ad25.2 + ad25.3 + ad50.1 + ad50.2 + ad50.3 + ad100.1 + ad100.2 + ad100.3 + ba25.1 + ba25.2 + ba25.3 + ba50.1 + ba50.2 + ba50.3 + ba100.1 + ba100.2 + ba100.3 + ty25.7 + ty50.7 + ty100.7 + ad25.7 + ad50.7 + ad100.7 + ba25.7 + ba50.7 + ba100.7 | ty25 + ty50 + ty100 + ad25 + ad50 + ad100 + ba25 + ba50 + ba100 + ty25.4 + ty25.5 + ty25.6 + ty50.4 + ty50.5 + ty50.6 + ty100.4 + ty100.5 + ty100.6 + ad25.4 + ad25.5 + ad25.6 + ad50.4 + ad50.5 + ad50.6 + ad100.4 + ad100.5 + ad100.6 + ba25.4 + ba25.5 + ba25.6 + ba50.4 + ba50.5 + ba50.6 + ba100.4 + ba100.5 + ba100.6 + ty25.7 + ty50.7 + ty100.7 + ad25.7 + ad50.7 + ad100.7 + ba25.7 + ba50.7 + ba100.7, data = data4)
summary(fit3)
```

## Lowest level IV: Hausman instruments 

Estimate the lowest level of the model using IV, using Hausman instruments
for price.

```{r}
data5 <- data2
data5 = data5[FALSE,]
for (i in unique(data2$week)){
  for (j in unique(data2$brand_name)){
    for (k in unique(data2$size)){
    test <- filter(data2, brand_name == j, week == i, size == k) 
    test <- test %>% mutate(avgp = (sum(test$price)-price)/(nrow(test)-1))
    data5 <- rbind(data5, test)
    }}}
data6 <- data5
data6 = data6[FALSE,]
for (i in unique(data5$week)){
  for (j in unique(data$store)){
    test <- filter(data5, week == i, store == j)
    test <- test %>% mutate(ty25h = avgp[1],ty50h = avgp[2], ty100h = avgp[3], ad25h = avgp[4], ad50h = avgp[5], ad100h = avgp[6], ba25h = avgp[7], ba50h = avgp[8], ba100h = avgp[9])
    data6 <- rbind(data6, test)
  }
}

data6[,c(1:12,14:32,69:96,106)]<- NULL
# 27 interaction variables between hausman instrument and product dummies
n = 56
for (i in seq(2,4)){
  for (j in  seq(47,49)){
  data6[,n] = data6[,i]*data6[,j]
  n <- n + 1
  }
}

for (i in seq(5,7)){
  for (j in  seq(50,52)){
  data6[,n] = data6[,i]*data6[,j]
  n <- n + 1
  }
}

for (i in seq(8,10)){
  for (j in  seq(53,55)){
  data6[,n] = data6[,i]*data6[,j]
  n <- n + 1
  }
}


fit4 <- ivreg(exp_share ~ ty25 + ty50 + ty100 + ad25 + ad50 + ad100 + ba25 + ba50 + ba100 + ty25.1 + ty25.2 + ty25.3 + ty50.1 + ty50.2 + ty50.3 + ty100.1 + ty100.2 + ty100.3 + ad25.1 + ad25.2 + ad25.3 + ad50.1 + ad50.2 + ad50.3 + ad100.1 + ad100.2 + ad100.3 + ba25.1 + ba25.2 + ba25.3 + ba50.1 + ba50.2 + ba50.3 + ba100.1 + ba100.2 + ba100.3 + ty25.7 + ty50.7 + ty100.7 + ad25.7 + ad50.7 + ad100.7 + ba25.7 + ba50.7 + ba100.7 | ty25 + ty50 + ty100 + ad25 + ad50 + ad100 + ba25 + ba50 + ba100 + ty25.4 + ty25.5 + ty25.6 + ty50.4 + ty50.5 + ty50.6 + ty100.4 + ty100.5 + ty100.6 + ad25.4 + ad25.5 + ad25.6 + ad50.4 + ad50.5 + ad50.6 + ad100.4 + ad100.5 + ad100.6 + ba25.4 + ba25.5 + ba25.6 + ba50.4 + ba50.5 + ba50.6 + ba100.4 + ba100.5 + ba100.6 + ty25.7 + ty50.7 + ty100.7 + ad25.7 + ad50.7 + ad100.7 + ba25.7 + ba50.7 + ba100.7, data = data6)
summary(fit4)
```

## Middle level IV

```{r}
# start with a new set of data
data7 <- data2
data7= data7[FALSE,]

for (i in unique(data2$week)){
  for (j in unique(data2$store)){
    test <- filter(data2, week == i, store == j)
    
    total1 = test$sales[1] + test$sales[2] + test$sales[3]
    total2 =test$sales[4] + test$sales[5] + test$sales[6]
    total3 = test$sales[7] + test$sales[8] + test$sales[9]
    
    test <- test[-c(2,3,5, 6,8,9),]
    
    test[,c(15:105)]<- NULL
    
    test <- test %>% mutate(totalq = ifelse(brand_name == "Tylenol", total1, ifelse(brand_name == "Advil", total2, ifelse(brand_name == "Bayer",total3, "NA")))) 
    
    test$totalq = as.numeric(as.character(test$totalq))
    
    test <- test %>% mutate(ty = ifelse(brand_name == "Tylenol", 1, 0),
                            ad = ifelse(brand_name == "Advil",1,0),
                            ba = ifelse(brand_name == "Bayer",1,0)) %>% mutate(exp_total2 = (sum(exp_total))) %>% mutate(stone_ty = test$stone[1],
                            stone_ad = test$stone[2],
                            stone_ba = test$stone[3])
      
    
    data7<- rbind(data7,test)
    
  }}  

n = 23
for (i in seq(16,18)){
  for (j in  seq(20,22)){
  data7[,n] = data7[,i]*data7[,j]
  n <- n + 1
  }
}
for (i in seq(16,18)){
  data7[,n] = data7[,i]*log(data7[,19])
  n <- n + 1
}

fit5 <- lm(log(totalq) ~ ty + ad + ba + ty.1 + ty.2 + ty.3 + ad.1 + ad.2 + ad.3 + ba.1 + ba.2 + ba.3 + ty.4 + ad.4 + ba.4,data7)
summary(fit5)
```

## Top level

```{r}
data8 <- data7
data8= data8[FALSE,]
income <- read_csv("OTC_Incomes.csv")

for (i in unique(data7$week)){
  for (j in unique(data7$store)){
    test <- filter(data7, week == i, store == j)
    income2 <- filter(income,week == i, store == j)
    
    test <- test %>% mutate(exp_share2 = exp_total/exp_total2) 
    test <- test %>% mutate(overallstone = sum(test$exp_share2*test$stone))
    test <- test %>% mutate(income = income2$average_income[1])
    
    test <- test[-c(2,3),]
    
    data8<- rbind(data8,test)
    
  }}  
data8[,c(4:9,11:14,16:18,20:34)]<- NULL


data8 <- cbind(data8,income)

fit6 <- lm(log(sales_total)~overallstone+income, data8)
summary(fit6)
```

## Compare across the models

The model using the Hausman instrument is the most valid one. This is determined by looking at the sign of the estimated coefficients for the nine different own price elasticities. 

For the original OLS model, own price elasticities: 6 out of 9 are negative.
For the IV model with wholesale price as instrument, 4 out of 9 are negative.
For the IV model with Hausman instrument, 7 out of 9 are negative. Therefore, the third model is the preferred specification. Its estimated coefficients will also be used to calculate the following conditional and unconditional elasticities.

```{r}
# average expenditure share for 9 products
omega_i <- c(mean(ty25$exp_share), mean(ty50$exp_share),mean(ty100$exp_share),mean(ad25$exp_share),mean(ad50$exp_share),mean(ad100$exp_share),mean(ba25$exp_share),mean(ba50$exp_share),mean(ba100$exp_share))

data9 <- data7
data9 <- data9 %>% mutate(exp_share2 = exp_total/exp_total2)
ty1 <- filter(data9, brand_name == "Tylenol")
omega_ty = mean(ty1$exp_share2)
ad1 <- filter(data9, brand_name == "Advil")
omega_ad = mean(ad1$exp_share2)
ba1 <- filter(data9, brand_name == "Bayer")
omega_ba = mean(ba1$exp_share2)

# average expenditrue share for 3 segments
omega_g <- c(omega_ty,omega_ad,omega_ba)

coef <- fit4$coefficients
coef <- as.data.frame(coef)
beta_i <- coef$coef[38:46]
gamma_ij <- coef$coef[11:37]
```

## conditional elasticities:

### Conditional Tyelenol

```{r}
## Tylenol25 with 25, 50, 100
  ty25_25 = (1/omega_i[1])*(gamma_ij[1]+gamma_ij[1]-beta_i[1]*omega_i[1])-1
  ty25_50 = (1/omega_i[1])*(gamma_ij[2]+gamma_ij[4]-beta_i[1]*omega_i[2])
  ty25_100 = (1/omega_i[1])*(gamma_ij[3]+gamma_ij[7]-beta_i[1]*omega_i[3])
## Tylenol50 with 25, 50, 100
  ty50_25 = (1/omega_i[2])*(gamma_ij[2]+gamma_ij[4]-beta_i[2]*omega_i[1])
  ty50_50 = (1/omega_i[2])*(gamma_ij[5]+gamma_ij[5]-beta_i[2]*omega_i[2])-1
  ty50_100 = (1/omega_i[2])*(gamma_ij[6]+gamma_ij[8]-beta_i[2]*omega_i[3])
## Tylenol100 with 25, 50, 100
  ty100_25 = (1/omega_i[3])*(gamma_ij[3]+gamma_ij[7]-beta_i[3]*omega_i[1])
  ty100_50 = (1/omega_i[3])*(gamma_ij[6]+gamma_ij[8]-beta_i[3]*omega_i[2])
  ty100_100 = (1/omega_i[3])*(gamma_ij[9]+gamma_ij[9]-beta_i[3]*omega_i[3])-1
con_ty <- c(ty25_25,ty25_50,ty25_100,ty50_25,ty50_50,ty50_100,ty100_25,ty100_50,ty100_100)
dim(con_ty) <- c(3,3)
con_ty
```

### Conditional Advil

```{r}
## Advil25 with 25, 50, 100
  ad25_25 = (1/omega_i[4])*(gamma_ij[10]+gamma_ij[10]-beta_i[4]*omega_i[4])-1
  ad25_50 = (1/omega_i[4])*(gamma_ij[2+9]+gamma_ij[4+9]-beta_i[4]*omega_i[5])
  ad25_100 = (1/omega_i[4])*(gamma_ij[12]+gamma_ij[16]-beta_i[4]*omega_i[6])
## Advil50 with 25, 50, 100
  ad50_25 = (1/omega_i[5])*(gamma_ij[11]+gamma_ij[13]-beta_i[5]*omega_i[4])
  ad50_50 = (1/omega_i[5])*(gamma_ij[14]+gamma_ij[14]-beta_i[5]*omega_i[5])-1
  ad50_100 = (1/omega_i[5])*(gamma_ij[15]+gamma_ij[17]-beta_i[5]*omega_i[6])
## Advil100 with 25, 50, 100
  ad100_25 = (1/omega_i[6])*(gamma_ij[12]+gamma_ij[16]-beta_i[6]*omega_i[4])
  ad100_50 = (1/omega_i[6])*(gamma_ij[15]+gamma_ij[17]-beta_i[6]*omega_i[5])
  ad100_100 = (1/omega_i[6])*(gamma_ij[18]+gamma_ij[18]-beta_i[6]*omega_i[6])-1
con_ad <- c(ad25_25,ad25_50,ad25_100,ad50_25,ad50_50,ad50_100,ad100_25,ad100_50,ad100_100)
dim(con_ad) <- c(3,3)
con_ad
```

### Conditional Bayer

```{r}
## Bayer25 with 25, 50, 100
  ba25_25 = (1/omega_i[7])*(gamma_ij[19]+gamma_ij[19]-beta_i[7]*omega_i[7])-1
  ba25_50 = (1/omega_i[7])*(gamma_ij[20]+gamma_ij[22]-beta_i[7]*omega_i[8])
  ba25_100 = (1/omega_i[7])*(gamma_ij[21]+gamma_ij[25]-beta_i[7]*omega_i[9])
## Bayer50 with 25, 50, 100
  ba50_25 = (1/omega_i[8])*(gamma_ij[20]+gamma_ij[22]-beta_i[8]*omega_i[7])
  ba50_50 = (1/omega_i[8])*(gamma_ij[23]+gamma_ij[23]-beta_i[8]*omega_i[8])-1
  ba50_100 = (1/omega_i[8])*(gamma_ij[24]+gamma_ij[26]-beta_i[8]*omega_i[9])
## Bayer100 with 25, 50, 100
  ba100_25 = (1/omega_i[9])*(gamma_ij[21]+gamma_ij[25]-beta_i[9]*omega_i[7])
  ba100_50 = (1/omega_i[9])*(gamma_ij[14]+gamma_ij[26]-beta_i[9]*omega_i[8])
  ba100_100 = (1/omega_i[9])*(gamma_ij[27]+gamma_ij[27]-beta_i[9]*omega_i[9])-1
con_ba <- c(ba25_25,ba25_50,ba25_100,ba50_25,ba50_50,ba50_100,ba100_25,ba100_50,ba100_100)
dim(con_ba) <- c(3,3)
con_ba
```

## Unconditional elasticities:

### Unconditional Tyelenol

```{r}
delta_1 = fit6$coefficients[2]
beta_g = fit5$coefficients[14:16]

## Unconditional Tylenol25 with 25, 50, 100
  ty25_25_Xg_Pj = omega_i[1]*(1+omega_g[1])+beta_g[1]*(omega_g[1]*omega_i[1])*(1+delta_1)
  ty25_25_un = (1/omega_i[1])*(gamma_ij[1]+gamma_ij[1])+beta_i[1]*(ty25_25_Xg_Pj-omega_i[1])-1+ty25_25_Xg_Pj
  ty25_50_Xg_Pj = omega_i[2]*(1+omega_g[1])+beta_g[1]*(omega_g[1]*omega_i[2])*(1+delta_1)
  ty25_50_un = (1/omega_i[1])*(gamma_ij[2]+gamma_ij[4])+beta_i[1]*(ty25_50_Xg_Pj-omega_i[2])+ty25_50_Xg_Pj
  ty25_100_Xg_Pj = omega_i[3]*(1+omega_g[1])+beta_g[1]*(omega_g[1]*omega_i[3])*(1+delta_1)
  ty25_100_un = (1/omega_i[1])*(gamma_ij[3]+gamma_ij[7])+beta_i[1]*(ty25_100_Xg_Pj-omega_i[3])+ty25_100_Xg_Pj
  
  
## Unconditional Tylenol50 with 25, 50, 100
  ty50_25_Xg_Pj = omega_i[1]*(1+omega_g[1])+beta_g[1]*(omega_g[1]*omega_i[1])*(1+delta_1)
  ty50_25_un = (1/omega_i[2])*(gamma_ij[2]+gamma_ij[4])+beta_i[2]*(ty50_25_Xg_Pj-omega_i[1])+ty50_25_Xg_Pj
  ty50_50_Xg_Pj = omega_i[2]*(1+omega_g[1])+beta_g[1]*(omega_g[1]*omega_i[2])*(1+delta_1)
  ty50_50_un = (1/omega_i[2])*(gamma_ij[5]+gamma_ij[5])+beta_i[2]*(ty50_50_Xg_Pj-omega_i[2])+ty50_50_Xg_Pj-1
  ty50_100_Xg_Pj = omega_i[3]*(1+omega_g[1])+beta_g[1]*(omega_g[1]*omega_i[3])*(1+delta_1)
  ty50_100_un = (1/omega_i[2])*(gamma_ij[6]+gamma_ij[8])+beta_i[2]*(ty50_100_Xg_Pj-omega_i[3])+ty50_100_Xg_Pj
  
## Unconditional Tylenol100 with 25, 50, 100
  ty100_25_Xg_Pj = omega_i[1]*(1+omega_g[1])+beta_g[1]*(omega_g[1]*omega_i[1])*(1+delta_1)
  ty100_25_un = (1/omega_i[3])*(gamma_ij[3]+gamma_ij[7])+beta_i[3]*(ty100_25_Xg_Pj-omega_i[1])+ty100_25_Xg_Pj
  ty100_50_Xg_Pj = omega_i[2]*(1+omega_g[1])+beta_g[1]*(omega_g[1]*omega_i[2])*(1+delta_1)
  ty100_50_un = (1/omega_i[3])*(gamma_ij[6]+gamma_ij[8])+beta_i[3]*(ty100_50_Xg_Pj-omega_i[2])+ty100_50_Xg_Pj
  ty100_100_Xg_Pj = omega_i[3]*(1+omega_g[1])+beta_g[1]*(omega_g[1]*omega_i[3])*(1+delta_1)
  ty100_100_un = (1/omega_i[3])*(gamma_ij[9]+gamma_ij[9])+beta_i[3]*(ty100_100_Xg_Pj-omega_i[3])+ty100_100_Xg_Pj-1
uncon_ty <- c(ty25_25_un,ty25_50_un,ty25_100_un,ty50_25_un,ty50_50_un,ty50_100_un,ty100_25_un,ty100_50_un,ty100_100_un)
dim(uncon_ty) <- c(3,3)
uncon_ty
```

### Unconditional Advil


```{r}
ad_Xg_Pj_25 = omega_i[4]*(1+omega_g[2])+beta_g[2]*(omega_g[2]*omega_i[4])*(1+delta_1)
ad_Xg_Pj_50 = omega_i[5]*(1+omega_g[2])+beta_g[2]*(omega_g[2]*omega_i[5])*(1+delta_1)
ad_Xg_Pj_100 = omega_i[6]*(1+omega_g[2])+beta_g[2]*(omega_g[2]*omega_i[6])*(1+delta_1)

## Unconditional Advil25 with 25, 50, 100
  ad25_25_un = (1/omega_i[4])*(gamma_ij[10]+gamma_ij[10])+beta_i[4]*(ad_Xg_Pj_25-omega_i[4])-1+ad_Xg_Pj_25
  ad25_50_un = (1/omega_i[4])*(gamma_ij[11]+gamma_ij[13])+beta_i[4]*(ad_Xg_Pj_50-omega_i[5])+ad_Xg_Pj_50
  ad25_100_un = (1/omega_i[4])*(gamma_ij[12]+gamma_ij[16])+beta_i[4]*(ad_Xg_Pj_100-omega_i[6])+ad_Xg_Pj_100
  
  
## Unconditional Advil50 with 25, 50, 100
  ad50_25_un = (1/omega_i[5])*(gamma_ij[11]+gamma_ij[13])+beta_i[5]*(ad_Xg_Pj_25-omega_i[4])+ad_Xg_Pj_25
  ad50_50_un = (1/omega_i[5])*(gamma_ij[14]+gamma_ij[14])+beta_i[5]*(ad_Xg_Pj_50-omega_i[5])+ad_Xg_Pj_50-1
  ad50_100_un = (1/omega_i[5])*(gamma_ij[15]+gamma_ij[17])+beta_i[5]*(ad_Xg_Pj_100-omega_i[6])+ad_Xg_Pj_100
  
## Unconditional Advil100 with 25, 50, 100
  ad100_25_un = (1/omega_i[6])*(gamma_ij[12]+gamma_ij[16])+beta_i[6]*(ad_Xg_Pj_25-omega_i[4])+ad_Xg_Pj_25
  ad100_50_un = (1/omega_i[6])*(gamma_ij[15]+gamma_ij[17])+beta_i[6]*(ad_Xg_Pj_50-omega_i[5])+ad_Xg_Pj_50
  ad100_100_un = (1/omega_i[6])*(gamma_ij[18]+gamma_ij[18])+beta_i[6]*(ad_Xg_Pj_100-omega_i[6])+ad_Xg_Pj_100-1
uncon_ad<- c(ad25_25_un,ad25_50_un,ad25_100_un,ad50_25_un,ad50_50_un,ad50_100_un,ad100_25_un,ad100_50_un,ad100_100_un)
dim(uncon_ad) <- c(3,3)
uncon_ad
```

### Unconditional Bayer

```{r}
ba_Xg_Pj_25 = omega_i[7]*(1+omega_g[3])+beta_g[3]*(omega_g[3]*omega_i[7])*(1+delta_1)
ba_Xg_Pj_50 = omega_i[8]*(1+omega_g[3])+beta_g[3]*(omega_g[3]*omega_i[8])*(1+delta_1)
ba_Xg_Pj_100 = omega_i[9]*(1+omega_g[3])+beta_g[3]*(omega_g[3]*omega_i[9])*(1+delta_1)

## Unconditional Advil25 with 25, 50, 100
  ba25_25_un = (1/omega_i[7])*(gamma_ij[19]+gamma_ij[19])+beta_i[7]*(ba_Xg_Pj_25-omega_i[7])-1+ba_Xg_Pj_25
  ba25_50_un = (1/omega_i[7])*(gamma_ij[20]+gamma_ij[22])+beta_i[7]*(ba_Xg_Pj_50-omega_i[8])+ba_Xg_Pj_50
  ba25_100_un = (1/omega_i[7])*(gamma_ij[21]+gamma_ij[25])+beta_i[7]*(ba_Xg_Pj_100-omega_i[9])+ba_Xg_Pj_100
  
## Unconditional Advil50 with 25, 50, 100
  ba50_25_un = (1/omega_i[8])*(gamma_ij[20]+gamma_ij[22])+beta_i[8]*(ba_Xg_Pj_25-omega_i[7])+ba_Xg_Pj_25
  ba50_50_un = (1/omega_i[8])*(gamma_ij[23]+gamma_ij[23])+beta_i[8]*(ba_Xg_Pj_50-omega_i[8])+ba_Xg_Pj_50-1
  ba50_100_un = (1/omega_i[8])*(gamma_ij[24]+gamma_ij[26])+beta_i[8]*(ba_Xg_Pj_100-omega_i[9])+ba_Xg_Pj_100
  
## Unconditional Advil100 with 25, 50, 100
  ba100_25_un = (1/omega_i[9])*(gamma_ij[21]+gamma_ij[25])+beta_i[9]*(ba_Xg_Pj_25-omega_i[7])+ba_Xg_Pj_25
  ba100_50_un = (1/omega_i[9])*(gamma_ij[24]+gamma_ij[26])+beta_i[9]*(ba_Xg_Pj_50-omega_i[8])+ba_Xg_Pj_50
  ba100_100_un = (1/omega_i[9])*(gamma_ij[27]+gamma_ij[27])+beta_i[9]*(ba_Xg_Pj_100-omega_i[9])+ba_Xg_Pj_100-1
  
uncon_ba<- c(ba25_25_un,ba25_50_un,ba25_100_un,ba50_25_un,ba50_50_un,ba50_100_un,ba100_25_un,ba100_50_un,ba100_100_un)
dim(uncon_ba) <- c(3,3)
uncon_ba
```

